How simple consensus to the mean can be mistaken for ``group polarization'' extremity-shifted consensus

### 2022-07-07 GroupPolarizationStatmod/papers/ms.tex
updated Hogg1990 supplement

@@

\paragraph{\citet{Hogg1990}} It is not clear if there are indeed significant pre-post
deliberation differences reported in this paper. The Results are a tangle of
estimates of effect sizes and diagnostic statistical measures. It is also
not clear that they actually report the pre- and post-deliberation opinions;
it appears they only report the shifts. ``Opinion Difference Measures'' 
does not seem to include a test that the shifts themselves are reliable.

>>>>

Different group polarization studies have different goals, and measure shifts
in a variety of ways, using different (or no) statistical tests to confirm
the presence of group polarization opinion shifts. This supplemental section
reviews the ten papers one-by-one and explains how group 
polarization was measured in each paper. I also explain how I decided which
group polarization detections I included from each paper, and how we decided
if they were plausibly false positives, including whether we needed to

@@

\paragraph{\citet{Hogg1990}} It is not clear if there are indeed significant
pre-post deliberation differences reported in this paper. The Results are a
tangle of estimates of effect sizes and diagnostic statistical measures. It
is also not clear that they actually report the pre- and post-deliberation
opinions; it appears they only report the shifts. ``Opinion Difference
Measures'' does not seem to include a test that the shifts themselves are
reliable. I decided to count a finding from this study as a false positive if
the model generated pre- and post-deliberation mean opinions within an
absolute error of 0.01 of the reported value. The argument seems to be that
since they are testing social ``frame[s] of reference'' (Table 1) that it is
not necessary to show that group polarization itself occurs, only that the
various experimental treatments yield different shifts---but if the shifts
themselves are insignificant, then what is being measured, exactly?
